26 Years of Water Quality Change in Rhode Island Lakes and Ponds

### 2019-01-29 manuscript/manuscript.Rmd
started adding in citation fig numbers to trend figures.

*`r fig_num(name = "temp_ri", caption = "Yearly trend over 20+ years of lake temperature in Rhode Island lakes and ponds.")`*

@@

*`r fig_num(name = "tn_ri", caption = "Yearly trend over 20+ years of Total Nitrogen (average z-score) in Rhode Island lakes and ponds.")`*

>>>>

(`r fig_num(name = "temp_ri", caption = "Yearly trend over 20+ years of lake temperature in Rhode Island lakes and ponds.", display = "cite")`).

*`r fig_num(name = "temp_ri")`*

@@

(`r fig_num(name = "tn_ri", caption = "Yearly trend over 20+ years of Total Nitrogen (average z-score) in Rhode Island lakes and ponds.", display = "cite")`).

*`r fig_num(name = "tn_ri")`*
